# Reproducible Research: Peer Assessment 1


## Loading and preprocessing the data

```{r,echo=TRUE}
setwd("C:/Disk A/Different/Economentrics/Coursera/Reprodusible research")
activitydata<-read.csv("./activity.csv", header=TRUE)
head(activitydata)
```


## What is mean total number of steps taken per day?
Calculate mean and median
```{r,echo=TRUE}
agg_by_date <-aggregate(activitydata$steps, by=list(date=activitydata$date),  FUN=mean,na.rm=TRUE)  
mean(agg_by_date$x,na.rm=TRUE)
median(agg_by_date$x,na.rm=TRUE)
```
Make a histogram of the total number of steps taken each day

```{r,echo=TRUE}
         
library(datasets)
hist(agg_by_date$x,xlab="steps be date",ylab="frequency",main="Histogram of total number of steps taken each day")
```

## What is the average daily activity pattern?
Make a time series plot (i.e. type = "l") of the 5-minute interval (x-axis) and the average number of steps taken, averaged across all days (y-axis)
```{r,echo=TRUE}
agg_by_interval <-aggregate(activitydata$steps, by=list(interv=activitydata$interval),  FUN=mean,na.rm=TRUE)  
agg_by_interval$index<-agg_by_interval$interv/5

plot(agg_by_interval$index,agg_by_interval$x,main="Time series plot",type="l", 
     pch=16,xlab="daily interval",ylab="Average number of steps")
```
#Which 5-minute interval, on average across all the days in the dataset, contains the maximum number of steps?
```{r,echo=TRUE}
subset(agg_by_interval,agg_by_interval$x==max(agg_by_interval$x,na.rm=TRUE))$index
```

## Imputing missing values
Total number of N/A's
```{r, echo=TRUE}
for (Var in names(activitydata)) {
        missing <- sum(is.na(activitydata[,Var]))
        if (missing > 0) {
                print(c(Var,missing))
        }
}

```



## Are there differences in activity patterns between weekdays and weekends?
