# Reproducible Research: Peer Assessment 1


## Loading and preprocessing the data

```{r,echo=TURE}
setwd("C:/Disk A/Different/Economentrics/Coursera/Reprodusible research")
activitydata<-read.csv("./activity.csv", header=TRUE)
head(activitydata)
```


## What is mean total number of steps taken per day?
Calculate mean and median
```{r,echo=TURE}
mean(agg_by_date$x,na.rm=TRUE)
median(agg_by_date$x,na.rm=TRUE)
```
Make a histogram of the total number of steps taken each day

```{r,echo=TRUE}
agg_by_date <-aggregate(activitydata$steps, by=list(date=activitydata$date),  FUN=mean,na.rm=TRUE)               
print(agg_by_date)
library(datasets)
hist(agg_by_date$x,xlab="steps be date",ylab="frequency",main="Histogram of total number of steps taken each day")
```

## What is the average daily activity pattern?
Make a time series plot (i.e. type = "l") of the 5-minute interval (x-axis) and the average number of steps taken, averaged across all days (y-axis)
```{r,echo=TRUE}
agg_by_interval <-aggregate(activitydata$steps, by=list(interv=activitydata$interval),  FUN=mean,na.rm=TRUE)  
print(agg_by_interval)
agg_by_interval$index<-agg_by_interval$interv/5

plot(agg_by_interval$index,agg_by_interval$x,main="Time series plot",type="l", 
     pch=16,xlab="daily interval",ylab="Average number of steps")
```


## Imputing missing values



## Are there differences in activity patterns between weekdays and weekends?
